Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-04-18 MAIN.tex
[MGa] some rephrasing
[MGa] stochastic OCP
[MM] constraints formulation (first try)
[MGa] TV-LQR, first version
[MM] DOCP re-formulation
[MGa] also my open loop figure
Let's see...

\newcommand{\cedpage}{\newpage{\thispagestyle{empty}\cleardoublepage}}
\usepackage{algorithm,algpseudocode}
\usepackage{tikz,tikz-3dplot}
\usetikzlibrary{arrows.meta,angles}

@@

\author{Martino Gulisano\textsuperscript{a}, Matteo Masoni\textsuperscript{a}, and \name{Marco Gabiccini\textsuperscript{a,*}
\thanks{* Contact: Marco Gabiccini. Email: marco.gabiccini@unipi.it}
}\affil{
\textsuperscript{a} Dipartimento di Ingegneria Civile e Industriale,	Universit\`{a} di Pisa, Pisa, Italy.}
}

@@

%\tableofcontents
\input{intro}
\input{stochastic_vehicle_dynamics}
\input{open_loop_planning}
%for back-off calculations
\input{closed_loop_planning}
\input{performance_comparison}
\input{conclusions}

>>>>

\newcommand{\cedpage}{\newpage{\thispagestyle{empty}\cleardoublepage}}
\usepackage{algorithm,algpseudocode}
\usepackage{tikz,tikz-3dplot}
\usetikzlibrary{arrows.meta,angles,decorations.pathmorphing,patterns}

\usepackage{bm}

@@

\author{Martino Gulisano\textsuperscript{a}, Matteo Masoni\textsuperscript{a}, \name{Marco Gabiccini\textsuperscript{a,*} and Massimo Guiggiani\textsuperscript{a}
\thanks{* Contact: Marco Gabiccini. Email: marco.gabiccini@unipi.it}
}\affil{
\textsuperscript{a} Dipartimento di Ingegneria Civile e Industriale,	Universit\`{a} di Pisa, Pisa, Italy.}
}

@@

%\tableofcontents
\input{intro}
\input{stochastic_vehicle_dynamics}
\input{marco_open_loop_planning}
%for back-off calculations
\input{closed_loop_planning}
\input{performance_comparison}
\input{conclusions}

### 2025-04-18 marco_open_loop_planning.tex
[MGa] also my open loop figure
Let's see...

\begin{figure}
	\centering
	\begin{tikzpicture}[%
		smallnode/.style={%
			circle, draw, minimum size=3mm, inner sep=0pt
		},
		r_smallnode/.style={%
			circle, draw, minimum size=3mm, inner sep=0pt, red
		},
		g_smallnode/.style={%
			circle, draw, minimum size=3mm, inner sep=0pt, mygreen
		},
		every path/.style={->, thick},
		x=1.5cm, y=1.5cm
		]

		\newcommand{\Plab}[2]{\bP^{#2}_{#1}}
		\definecolor{mygreen}{RGB}{0 150 0}

		% Nodes
		% First row
		\node[smallnode, label={[label distance=-2pt]above:\protect\(\Plab{k-2}{H-2}\)}] (Pk-2H-2) at (1,0) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k-1}{H-1}\)}] (Pk-1H-1) at (2,0) {};
		\node[g_smallnode, label={[label distance=-2pt]above:\(\Plab{k}{H}\)}] (PkH) at (3,0) {};
		\node[r_smallnode, label={[label distance=-2pt]above:\(\Plab{k+1}{0}\)}] (Pk+10) at (4,0) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+2}{1}\)}] (Pk+21) at (5,0) {};

		% Second row
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k-2}{H-3}\)}] (Pk-2H-3) at (1,1) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k-1}{H-2}\)}] (Pk-1H-2) at (2,1) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k}{H-1}\)}] (PkH-1) at (3,1) {};
		\node[g_smallnode, label={[label distance=-2pt]above:\(\Plab{k+1}{H}\)}] (Pk+1H) at (4,1) {};
		\node[r_smallnode, label={[label distance=-2pt]above:\(\Plab{k+2}{0}\)}] (Pk+20) at (5,1) {};

		% dots row
		\node[label={center,rotate=90:\(\dots\)}] (dots2) at (1, 1.7) {};
		\node[label={center,rotate=90:\(\dots\)}] (dots3) at (2, 1.7) {};
		\node[label={center,rotate=90:\(\dots\)}] (dots4) at (3, 1.7) {};
		\node[label={center,rotate=90:\(\dots\)}] (dots5) at (4, 1.7) {};
		\node[label={center,rotate=90:\(\dots\)}] (dots6) at (5, 1.7) {};

		% Third row
		\node[g_smallnode, label={[label distance=-2pt]above:\(\Plab{k-2}{H}\)}] (Pk-2H) at (1,2) {};
		\node[r_smallnode, label={[label distance=-2pt]above:\(\Plab{k-1}{0}\)}] (Pk-10) at (2,2) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k}{1}\)}] (Pk1) at (3,2) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+1}{2}\)}] (Pk+12) at (4,2) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+2}{3}\)}] (Pk+23) at (5,2) {};

		% Fourth row
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k-2}{H-1}\)}] (Pk-2H-1) at (1,3) {};
		\node[g_smallnode, label={[label distance=-2pt]above:\(\Plab{k-1}{H}\)}] (Pk-1H) at (2,3) {};
		\node[r_smallnode, label={[label distance=-2pt]above:\(\Plab{k}{0}\)}] (Pk0) at (3,3) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+1}{1}\)}] (Pk+11) at (4,3) {};
		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+2}{2}\)}] (Pk+22) at (5,3) {};

		% Curved arrows
		\draw[bend left=20] (Pk-2H-2) to (Pk-1H-1);
		\draw[bend left=20] (Pk-1H-1) to (PkH);
		\draw[bend left=20] (Pk+10) to (Pk+21);

		\draw[bend left=20] (Pk-2H-3) to (Pk-1H-2);
		\draw[bend left=20] (Pk-1H-2) to (PkH-1);
		\draw[bend left=20] (PkH-1) to (Pk+1H);

		\draw[bend left=20] (Pk-10) to (Pk1);
		\draw[bend left=20] (Pk1) to (Pk+12);
		\draw[bend left=20] (Pk+12) to (Pk+23);

		\draw[bend left=20] (Pk-10) to (Pk1);
		\draw[bend left=20] (Pk1) to (Pk+12);
		\draw[bend left=20] (Pk+12) to (Pk+23);

		\draw[bend left=20] (Pk-2H-1) to (Pk-1H);
		\draw[bend left=20] (Pk0) to (Pk+11);
		\draw[bend left=20] (Pk+11) to (Pk+22);

		% Dashed rectangle
		\draw[dashed, thick, rounded corners] (2.6,-.25) rectangle (3.4,3.5);

	\end{tikzpicture}
\caption{Schematic representation of the continuity and initialization equations associated with the $H+1$ propagated instances of the covariance matrix introduced in problem~\eqref{eq:DOCPopenloop}. The dashed rectangle highlights the $k$-th discretization step, at which the robust constraints are enforced. Each node corresponds to a specific covariance matrix, where the subscript denotes the current grid index and the superscript indicates the number of propagation steps since initialization. At each step, two key instances are emphasized: the matrix to be initialized at that step (red node), and the matrix that has been propagated over $H$ steps (green node), which is used in the evaluation of the constraint backoff.}
	%\caption{Schematic representation of the continuity and initialization Equations for the $H+1$ versions of the covariance matrix introduced in the discretized OCP. The dashed rectangle indicate the $k$-th step, in which the constraints are formulated. Each node represents a covariance matrix, labeled such that the subscript denotes the current grid step, while the superscript indicates the number of propagation steps it has undergone. At each step, two nodes are highlighted: the covariance matrix to be initialized (red node) and the matrix that has been propagated for $H$ steps (green node), which is used to formulate the robust constraints.}
	\label{fig:DOCPgrid}
\end{figure}

>>>>

\begin{figure}
	\centering
%\begin{tikzpicture}[%
%		smallnode/.style={%
%			circle, draw, minimum size=3mm, inner sep=0pt
%		},
%		r_smallnode/.style={%
%			circle, draw, minimum size=3mm, inner sep=0pt, red
%		},
%		g_smallnode/.style={%
%			circle, draw, minimum size=3mm, inner sep=0pt, mygreen
%		},
%		every path/.style={->, thick},
%		x=1.5cm, y=1.5cm
%		]
%		
%		\newcommand{\Plab}[2]{\bP^{#2}_{#1}}
%		\definecolor{mygreen}{RGB}{0 150 0}
%		
%		% Nodes
%		% First row
%		\node[smallnode, label={[label distance=-2pt]above:\protect\(\Plab{k-2}{H-2}\)}] (Pk-2H-2) at (1,0) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k-1}{H-1}\)}] (Pk-1H-1) at (2,0) {};
%		\node[g_smallnode, label={[label distance=-2pt]above:\(\Plab{k}{H}\)}] (PkH) at (3,0) {};
%		\node[r_smallnode, label={[label distance=-2pt]above:\(\Plab{k+1}{0}\)}] (Pk+10) at (4,0) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+2}{1}\)}] (Pk+21) at (5,0) {};
%		
%		% Second row
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k-2}{H-3}\)}] (Pk-2H-3) at (1,1) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k-1}{H-2}\)}] (Pk-1H-2) at (2,1) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k}{H-1}\)}] (PkH-1) at (3,1) {};
%		\node[g_smallnode, label={[label distance=-2pt]above:\(\Plab{k+1}{H}\)}] (Pk+1H) at (4,1) {};
%		\node[r_smallnode, label={[label distance=-2pt]above:\(\Plab{k+2}{0}\)}] (Pk+20) at (5,1) {};
%		
%		% dots row
%		\node[label={center,rotate=90:\(\dots\)}] (dots2) at (1, 1.7) {};
%		\node[label={center,rotate=90:\(\dots\)}] (dots3) at (2, 1.7) {};
%		\node[label={center,rotate=90:\(\dots\)}] (dots4) at (3, 1.7) {};
%		\node[label={center,rotate=90:\(\dots\)}] (dots5) at (4, 1.7) {};
%		\node[label={center,rotate=90:\(\dots\)}] (dots6) at (5, 1.7) {};
%		
%		% Third row
%		\node[g_smallnode, label={[label distance=-2pt]above:\(\Plab{k-2}{H}\)}] (Pk-2H) at (1,2) {};
%		\node[r_smallnode, label={[label distance=-2pt]above:\(\Plab{k-1}{0}\)}] (Pk-10) at (2,2) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k}{1}\)}] (Pk1) at (3,2) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+1}{2}\)}] (Pk+12) at (4,2) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+2}{3}\)}] (Pk+23) at (5,2) {};
%		
%		% Fourth row
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k-2}{H-1}\)}] (Pk-2H-1) at (1,3) {};
%		\node[g_smallnode, label={[label distance=-2pt]above:\(\Plab{k-1}{H}\)}] (Pk-1H) at (2,3) {};
%		\node[r_smallnode, label={[label distance=-2pt]above:\(\Plab{k}{0}\)}] (Pk0) at (3,3) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+1}{1}\)}] (Pk+11) at (4,3) {};
%		\node[smallnode, label={[label distance=-2pt]above:\(\Plab{k+2}{2}\)}] (Pk+22) at (5,3) {};
%		
%		% Curved arrows
%		\draw[bend left=20] (Pk-2H-2) to (Pk-1H-1);
%		\draw[bend left=20] (Pk-1H-1) to (PkH);
%		\draw[bend left=20] (Pk+10) to (Pk+21);
%		
%		\draw[bend left=20] (Pk-2H-3) to (Pk-1H-2);
%		\draw[bend left=20] (Pk-1H-2) to (PkH-1);
%		\draw[bend left=20] (PkH-1) to (Pk+1H);
%		
%		\draw[bend left=20] (Pk-10) to (Pk1);
%		\draw[bend left=20] (Pk1) to (Pk+12);
%		\draw[bend left=20] (Pk+12) to (Pk+23);
%		
%		\draw[bend left=20] (Pk-10) to (Pk1);
%		\draw[bend left=20] (Pk1) to (Pk+12);
%		\draw[bend left=20] (Pk+12) to (Pk+23);
%		
%		\draw[bend left=20] (Pk-2H-1) to (Pk-1H);
%		\draw[bend left=20] (Pk0) to (Pk+11);
%		\draw[bend left=20] (Pk+11) to (Pk+22);
%		
%		% Dashed rectangle
%		\draw[dashed, thick, rounded corners] (2.6,-.25) rectangle (3.4,3.5);
%		
%	\end{tikzpicture}
\definecolor{mygreen}{RGB}{0,150,0}
%\begin{tikzpicture}[
%    smallnode/.style={circle, draw, minimum size=3mm, inner sep=0pt},
%    r_smallnode/.style={circle, draw=red, minimum size=3mm, inner sep=0pt},
%    g_smallnode/.style={circle, draw=mygreen, minimum size=3mm, inner sep=0pt},
%    every path/.style={->, thick},
%    x=1.4cm, y=1.2cm
%]
%
%% Row j=0 (y = 3)
%\node[r_smallnode, label={[label distance=-2pt]above:\(\bP_0^0\)}] (P00) at (1,3) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_1^1\)}] (P11) at (2,3) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_2^2\)}] (P22) at (3,3) {};
%\node[g_smallnode, label={[label distance=-2pt]above:\(\bP_3^3\)}] (P33) at (4,3) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_4^4\)}] (P44) at (5,3) {};
%\node at (6,3) {\(\cdots\)};
%
%% Row j=1 (y = 2)
%\node[r_smallnode, label={[label distance=-2pt]above:\(\bP_1^0\)}] (P10) at (2,2) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_2^1\)}] (P21) at (3,2) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_3^2\)}] (P32) at (4,2) {};
%\node[g_smallnode, label={[label distance=-2pt]above:\(\bP_4^3\)}] (P43) at (5,2) {};
%\node at (6,2) {\(\cdots\)};
%
%% Row j=2 (y = 1)
%\node[r_smallnode, label={[label distance=-2pt]above:\(\bP_2^0\)}] (P20) at (3,1) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_3^1\)}] (P31) at (4,1) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_4^2\)}] (P42) at (5,1) {};
%\node[g_smallnode, label={[label distance=-2pt]above:\(\bP_5^3\)}] (P53) at (6,1) {};
%\node at (7,1) {\(\cdots\)};
%
%% Row j=3 (y = 0)
%\node[r_smallnode, label={[label distance=-2pt]above:\(\bP_3^0\)}] (P30) at (4,0) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_4^1\)}] (P41) at (5,0) {};
%\node[smallnode, label={[label distance=-2pt]above:\(\bP_5^2\)}] (P52) at (6,0) {};
%\node[g_smallnode, label={[label distance=-2pt]above:\(\bP_6^3\)}] (P63) at (7,0) {};
%\node at (8,0) {\(\cdots\)};
%
%% Arrows: P_k^j --> P_{k+1}^{j+1}
%\draw (P00) -- (P11);
%\draw (P11) -- (P22);
%\draw (P22) -- (P33);
%\draw (P33) -- (P44);
%
%\draw (P10) -- (P21);
%\draw (P21) -- (P32);
%\draw (P32) -- (P43);
%
%\draw (P20) -- (P31);
%\draw (P31) -- (P42);
%\draw (P42) -- (P53);
%
%\draw (P30) -- (P41);
%\draw (P41) -- (P52);
%\draw (P52) -- (P63);
%
%% Dashed box around column k = 3 (x=4)
%\draw[dashed, thick, rounded corners] (3.6,-0.5) rectangle (4.4,3.5);
%
%% Optional top axis labels
%\node at (1, 4.1) {\scriptsize \(k=0\)};
%\node at (2, 4.1) {\scriptsize \(k=1\)};
%\node at (3, 4.1) {\scriptsize \(k=2\)};
%\node at (4, 4.1) {\scriptsize \(k=3\)};
%\node at (5, 4.1) {\scriptsize \(k=4\)};
%\node at (6, 4.1) {\scriptsize \(k=5\)};
%\node at (7, 4.1) {\scriptsize \(k=6\)};
%
%\end{tikzpicture}

\begin{tikzpicture}[
    smallnode/.style={circle, draw, minimum size=3mm, inner sep=0pt},
    r_smallnode/.style={circle, draw=red, minimum size=3mm, inner sep=0pt},
    g_smallnode/.style={circle, draw=mygreen, minimum size=3mm, inner sep=0pt},
    r_hatnode/.style={
    circle, draw=red, pattern=north east lines, pattern color=red,
    minimum size=3mm, inner sep=0pt},
    g_hatnode/.style={
    circle, draw=mygreen, pattern=north east lines, pattern color=mygreen,
    minimum size=3mm, inner sep=0pt},
    every path/.style={->, thick},
    x=1.4cm, y=1.2cm
]

% ROW j = 0 (y=3)
\node[r_hatnode, label={[label distance=-2pt]above:\(\bP_{k-3}^0\)}] (P00) at (1,3) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k-2}^1\)}] (P11) at (2,3) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k-1}^2\)}] (P22) at (3,3) {};
\node[g_hatnode, label={[label distance=-2pt]above:\(\bP_k^3\)}] (P33) at (4,3) {};
\node[r_hatnode, label={[label distance=-2pt]above:\(\bP_{k+1}^0\)}] (P44) at (5,3) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k+2}^1\)}] (P55) at (6,3) {};

% ROW j = 1 (y=2)
\node[r_hatnode, label={[label distance=-2pt]above:\(\bP_{k-2}^0\)}] (P10) at (2,2) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k-1}^1\)}] (P21) at (3,2) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_k^2\)}] (P32) at (4,2) {};
\node[g_hatnode, label={[label distance=-2pt]above:\(\bP_{k+1}^3\)}] (P43) at (5,2) {};
\node[r_hatnode, label={[label distance=-2pt]above:\(\bP_{k+2}^0\)}] (P54) at (6,2) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k+3}^1\)}] (P65) at (7,2) {};

% ROW j = 2 (y=1)
\node[r_hatnode, label={[label distance=-2pt]above:\(\bP_{k-1}^0\)}] (P20) at (3,1) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_k^1\)}] (P31) at (4,1) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k+1}^2\)}] (P42) at (5,1) {};
\node[g_hatnode, label={[label distance=-2pt]above:\(\bP_{k+2}^3\)}] (P53) at (6,1) {};
\node[r_hatnode, label={[label distance=-2pt]above:\(\bP_{k+3}^0\)}] (P64) at (7,1) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k+4}^1\)}] (P75) at (8,1) {};

% ROW j = 3 (y=0)
\node[r_hatnode, label={[label distance=-2pt]above:\(\bP_k^0\)}] (P30) at (4,0) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k+1}^1\)}] (P41) at (5,0) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k+2}^2\)}] (P52) at (6,0) {};
\node[g_hatnode, label={[label distance=-2pt]above:\(\bP_{k+3}^3\)}] (P63) at (7,0) {};
\node[r_hatnode, label={[label distance=-2pt]above:\(\bP_{k+4}^0\)}] (P74) at (8,0) {};
\node[smallnode, label={[label distance=-2pt]above:\(\bP_{k+5}^1\)}] (P85) at (9,0) {};

% ARROWS
\draw (P00) -- (P11);
\draw (P11) -- (P22);
\draw (P22) -- (P33);
\draw (P22) -- (P33);

\draw (P44) -- (P55);
\draw[dashed,->] (P55) -- ++(1,0);

\draw (P10) -- (P21);
\draw (P21) -- (P32);
\draw (P32) -- (P43);
\draw (P54) -- (P65);
\draw[dashed,->] (P65) -- ++(1,0);

\draw (P20) -- (P31);
\draw (P31) -- (P42);
\draw (P42) -- (P53);
\draw (P64) -- (P75);
\draw[dashed,->] (P75) -- ++(1,0);

\draw (P30) -- (P41);
\draw (P41) -- (P52);
\draw (P52) -- (P63);

\draw (P74) -- (P85);
\draw[dashed,->] (P85) -- ++(1,0);

% Dashed box around column k (x=4)
\draw[dashed, thick, rounded corners] (3.6,-0.5) rectangle (4.4,3.7);

% Top axis labels
\node at (0, 4.3) {\scriptsize \(\cdots\)};
\node at (1, 4.3) {\scriptsize \(k-3\)};
\node at (2, 4.3) {\scriptsize \(k-2\)};
\node at (3, 4.3) {\scriptsize \(k-1\)};
\node (knode) at (4, 4.3) {\scriptsize \(k\)};
\node at (5, 4.3) {\scriptsize \(k+1\)};
\node at (6, 4.3) {\scriptsize \(k+2\)};
\node at (7, 4.3) {\scriptsize \(k+3\)};
\node at (8, 4.3) {\scriptsize \(k+4\)};
\node at (9, 4.3) {\scriptsize \(\cdots\)};

% Wiggly arrow from label to top edge of dashed box
\draw[->, thick, decorate, decoration={snake, amplitude=0.25mm, segment length=2.5mm}]
  (knode.south) -- (4, 3.8);

% Legend box (top right)
%\begin{scope}[shift={(6.5,2.5)}]
%    \node[r_smallnode] (r) at (0,0) {};
%    \node[anchor=west] at (0.4,0) {\scriptsize Initialized matrix \(\bP_k^0\)};
%
%    \node[g_smallnode] (g) at (0,-0.8) {};
%    \node[anchor=west] at (0.4,-0.8) {\scriptsize Most propagated matrix \(\bP_k^3\)};
%\end{scope}

\end{tikzpicture}

\caption{Cartoon representation (depicted for $H=3$) of the continuity and initialization equations associated with the $H+1$ propagated instances of the covariance matrix introduced in problem~\eqref{eq:DOCPopenloop}. The dashed rectangle highlights the $k$-th discretization step, at which the robust constraints are enforced. Each node corresponds to a specific covariance matrix, where the subscript denotes the current grid index and the superscript indicates the number of propagation steps since initialization. At each step, two key instances are emphasized: the matrix to be initialized at that step (red node), and the matrix that has been propagated over $H$ steps (green node), which is used in the evaluation of the constraint backoff.}
	%\caption{Schematic representation of the continuity and initialization Equations for the $H+1$ versions of the covariance matrix introduced in the discretized OCP. The dashed rectangle indicate the $k$-th step, in which the constraints are formulated. Each node represents a covariance matrix, labeled such that the subscript denotes the current grid step, while the superscript indicates the number of propagation steps it has undergone. At each step, two nodes are highlighted: the covariance matrix to be initialized (red node) and the matrix that has been propagated for $H$ steps (green node), which is used to formulate the robust constraints.}
	\label{fig:DOCPgrid}
\end{figure}
